A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-25 paper/main.tex
revision and formatting of 1st lvl analysis

% 1st lv}
\todo[inline]{What follows has typos}
We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (see Table \ref{tab:regressors}).
The 20 most often occuring detailed part-of-speech labels (\texttt{nn} with N=\rNnAll\space to text{prf} with N=\rPrfAll) were modelled as such from the onset to offset of each word\todo{This has errors that I do not know how to fix}.
The remaining labels were pooled to (\texttt{tag\_other}; N=\rTagotherAll)\todo{I do not know what this means}.
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) to be used as a nuisance regressors\todo{Does that mean they share events with "other"}.
The end of each complete grammatical sentence was modeled as an impulse event (N=\rSentenceAll)\todo{Why? Above it says 'we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns)'. What does this need sentences for?}.
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control condition were created by the following rationale:
events were fitted into longer lasting intervals between onsets and offsets of words assumed\todo{Why assumed? Isn't the point of the annotion to "know"?} to contain no audible speech.
Each event of the no-speech condition had to have a minimum distance of \unit[1.8]{s} to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
A length of \unit[70]{ms} was chosen for no-speech events matching the average length of phonemes.
Lastly, we used events\todo{They are not really events, but a continous nuisance regressor} reflecting low-level auditory features (left-right difference in volume and root mean squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
The Pearson correlation coefficients of the 26 regressors across the time course of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
Temporal derivatives were also included in the design matrix and the design was subjected to the same temporal filtering as the BOLD time series.
Finally, six motion parameters were used as additional nuisance regressors.

\todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}
The following three t-contrasts were defined:
% 1b) no-speech > words;
% 2b) coordinate conjunctions > proper nouns;
% 3b) coordinate conjunctions > nouns.
1) words (all 21 \texttt{tag}-related regressors; N=15985) > no-speech (\texttt{no-sp}; N=\rNospAll),
2) proper nouns (\texttt{ne}; N=\rNeAll) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
\todo[inline]{I think having the N here is confusion. It is a contrast between regressors models. The number of events only indirectly accounts for the variance (which is interesting here). I would strip this info to reduce confusion}
% implementation detail. Any analysis should preserve the orientiation.
%The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].

>>>>

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this means; hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
they share events with "other"}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
it says 'we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns)'. What does this need sentences for?}.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? => Words where chosen to carefully; intervals don't
contain any audible speech with 98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

\todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}

% t-contrasts
The following three t-contrasts were defined:
% 1b) no-speech > words;
% 2b) coordinate conjunctions > proper nouns;
% 3b) coordinate conjunctions > nouns.
1) words (all 21 \texttt{tag}-related regressors; N=15985) > no-speech (\texttt{no-sp}; N=\rNospAll),
2) proper nouns (\texttt{ne}; N=\rNeAll) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
\todo[inline]{I think having the N here is confusion. It is a contrast between regressors models. The number of events only indirectly accounts for the variance (which is interesting here). I would strip this info to reduce confusion}
% implementation detail. Any analysis should preserve the orientiation.
%The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
